%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{graphicx} % includegraphics command is implemented here
\input{glyphtounicode}


%----------FONT OPTIONS---------- 
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Shahbaz Ali} \\ \vspace{5pt}
    \small +92-321-4856934 $|$ \href{mailto:shahbazlization@gmail.com}{\underline{shahbazlization@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/shahbazlization/}{\underline{LinkedIn}} $|$
    \href{https://github.com/cricketjanoon?tab=repositories}{\underline{GitHub}} $|$
    \href{https://www.gravatar.com/avatar/7dde2b7c6bb458bc6e3acabc25400a3e?s=500}{\underline{Gravatar}} $|$
    \href{https://github.com/cricketjanoon/curriculum-vitae/blob/main/resume.pdf}{\underline{Updated Resume}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lahore University of Management Sciences, Lahore}{Lahore, Pakistan}
      {\textbf{MS Computer Science, CGPA 3.17}}{July 2019 - May 2021}
      \item \textbf{Courses:} Machine Learning, Design and Analysis of Algorithms, Deep Learning, Computer Vision, Advanced Operating System, Applied Probability, Digital Image Processing, Computer Architecture, Speech Processing, ICT4D
      
    \resumeSubheading
      {Government College University, Lahore}{Lahore, Pakistan}
      {\textbf{BS Computer Science, CGPA 3.43}}{Aug. 2014 -- May 2018}
      \item \textbf{Courses:} Operating Systems, Data Structures, Analysis Of Algorithms, Artificial Intelligence, Machine Learning, Networking, Databases, Theory of Automata, Compilers Construction
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart


    \resumeSubheading
      {Senior Software Engineer \text{\textbar} C++}  {Mar 2024 - Present}
      {Logiciel Services}{Remote}
      \resumeItemListStart
        \resumeItem{Optimized low-latency trading performance by tuning FIX engine parameters and enhancing message parsing, order routing, and execution speeds using advanced C++ techniques.
Leveraged Boost.Asio for asynchronous networking to improve system responsiveness and throughput.
Provided real-time production support, resolving FIX session issues, order rejections, and execution anomalies through detailed log analysis and debugging.}
        \resumeItem{Developed core components of the Signals Engine in C++, implementing technical indicators (EMA, SMA, MACD, RSI, Stochastic, Parabolic SAR) using TA-Lib.
Built pattern detection logic for candlestick, MACD, stochastic, and PSAR-based patterns, and integrated them to generate buy/sell signals based on configurable strategies.}
		\resumeItemListEnd
        \resumeSubheading
      {C Developer}  {Mar 2024 - Sep 2024}
      {Convsync}{Remote}
      \resumeItemListStart
        \resumeItem{This short term project focused on converting the legacy C code (30 years old) written in Ingress Framework using QUEL database language to modern technologies like Angular, Java, SQL etc.} \resumeItem{I contributed in interpreting the legacy code and providing the understanding to high-level language (Java) developers. The code was written in legacy framework more than 30 years ago and there was little to no documentation available.}
    \resumeItemListEnd

%    \resumeSubheading
%      {C Developer}{Mar 2024 - Sep 2024}
%      {Convsync, Pakistan}{Remote}
%      \resumeItemListStart
%        \resumeItem{Working as part-time C developer for Convsync which is working on a project for Skywater Technologies, Inc. }
%      \resumeItem{Responsibilities included converting legacy code and framework written in Quake C, E-QUEL and Ingress VIFRED framework in collaboration with Ingress db into documentation which is understandable for high-level language developers.}
%      \resumeItem{I documented the code and provided other developer with understanding of existing code and framework. The code was written more than 30 years ago.}
%        
%    \resumeItemListEnd


    \resumeSubheading
      {Senior Software Engineer \text{\textbar} C++}{Aug 2021 - Feb 2024}
      {Avanza Solutions}{Hybrid/Remote}
      \resumeItemListStart
        \resumeItem{Worked as a C++ Developer in the Electronic Funds Transfer (EFT) department.}
        \resumeItem{Worked on a product, \textbf{Rendezvous}, which is a middleware solution to incorporate multiple financial and non-financial channels i.e. Mobile, Internet Banking, POS, Credit/Debit Card Payment Systems, Core Banking, Loan Management Systems etc.}
        \resumeItem{Reponsibiliies included sending and receiving message over TCP/IP sockets to 1-link (which is national switch for IBFT payments in Pakistan)}
        \resumeItem{Worked for national and International Clients: KHCB (Bahrain), NRSP(Pakistan), F5(Dubai)}
        \resumeItem{Responsibilities included: Development and deployment of new financial or non-financial transactions, Unit Testing during development, Managing databases using SQL/Oracle.}
    \resumeItemListEnd
      
    \resumeSubheading
      {Teaching Assistant \text{\textbar} C, C++, Python, Matlab}{Jan 2020 - Jan 2022}
      {Lahore University of Management Sciences}{Lahore, Pakistan}
      \vspace{0.1cm}
      
      \resumeItemListStart
      During my 2 year of MS at LUMS, I worked as a TA for 5 graduate level courses and 1 undergraduate course. For these courses I designed and graded assignments/quizzes and also conducted tutorial sessions. The courses are:
        \resumeItem{CS-535 Machine Learning with Dr. Agha Ali Raza (Fall 2021)}
        \resumeItem{CS-623 Hardware Architecture for AI with Dr. Rehan Hameed (Spring 2021)}
        \resumeItem{CS-5317 Deep Learning with Dr. Murtaza Taj (Spring 2021)}
        \resumeItem{CS-510 Design and Analysis of Algorithm with Dr. Imdad Ullah Khan (Fall 2020)}
        \resumeItem{CS-535 Machine Learning with Dr. Agha Ali Raza (Spring 2020)}
        \resumeItem{CS-331 Artificial Intelligence with Dr. Mian Muhammad Awais (Spring 2020)}        
     \resumeItemListEnd      
      
%    \resumeSubheading
%      {Technical Content Engineer}{Feb 2021 - July 2021}
%      {Educative, Inc}{Lahore, Pakistan}
%      \resumeItemListStart
%        \resumeItem{Created/Managed difference courses on the platform}
%        \resumeItem{Played part in the review process of different courses}
%        \resumeItem{Conducted interviews and helped in the hiring process}
%    \resumeItemListEnd
      
    \resumeSubheading
      {Software Development Engineer \text{\textbar} C\#, Unity}{July 2018 - November 2019}
      {Skill Knight Studios}{Lahore, Pakistan}
      \resumeItemListStart
        \resumeItem{Worked on different cross platform mobile games. Mostly added features or updates to the games already published on Play Store and App Store.}
        \resumeItem{Maintained a match 3 game with large user base. Removal of bugs reported by users and also quarterly major/minor feature updates}
\resumeItemListEnd
    


      
% -----------Multiple Positions Heading-----------
    % \resumeSubSubheading
    % {Software Engineer I}{Oct 2014 - Sep 2016}
    % \resumeItemListStart
    %     \resumeItem{Apache Beam}
    %      {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
    % \resumeItemListEnd
    % \resumeSubHeadingListEnd
%-------------------------------------------

    % \resumeSubheading
    %   {Information Technology Support Specialist}{Sep. 2018 -- Present}
    %   {Southwestern University}{Georgetown, TX}
    %   \resumeItemListStart
    %     \resumeItem{Communicate with managers to set up campus computers used on campus}
    %     \resumeItem{Assess and troubleshoot computer problems brought by students, faculty and staff}
    %     \resumeItem{Maintain upkeep of computers, classroom equipment, and 200 printers across campus}
    % \resumeItemListEnd

    % \resumeSubheading
    %   {Artificial Intelligence Research Assistant}{May 2019 -- July 2019}
    %   {Southwestern University}{Georgetown, TX}
    %   \resumeItemListStart
    %     \resumeItem{Explored methods to generate video game dungeons based off of \emph{The Legend of Zelda}}
    %     \resumeItem{Developed a game in Java to test the generated dungeons}
    %     \resumeItem{Contributed 50K+ lines of code to an established codebase via Git}
    %     \resumeItem{Conducted  a human subject study to determine which video game dungeon generation technique is enjoyable}
    %     \resumeItem{Wrote an 8-page paper and gave multiple presentations on-campus}
    %     \resumeItem{Presented virtually to the World Conference on Computational Intelligence}
    %   \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
Most of the projects listed below were during my BS and MS educational tenure. Professional projects are listed above in the EXPERIENCE section.
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Inference for CNN model in C} $|$ \emph{C/C++}}{March, 2021}
          \resumeItemListStart
            \resumeItem{Trained the CNN on fashion-mnist dataset in Keras}
            \resumeItem{Saved the weights in binary files}
            \resumeItem{Then used this weights to make prediction in C code}
            \resumeItem{Implemented convolution, fully-connected, dropout, maxpool, relu and softmax layers in C}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Web Server (Linux)} $|$ \emph{C}}{March 2020}
          \resumeItemListStart
            \resumeItem{Primitive Multi-threaded Clients and Multi-threaded Server model }
            \resumeItem{Clients send a request(using socket programming), which is completed and acknowledged by Server}
          \resumeItemListEnd              
          
   
      \resumeProjectHeading
          {\textbf{File System (Linux)} $|$ \emph{C}}{May 2020}
          \resumeItemListStart
            \resumeItem{Basic file-system which has all basic functions like open(), close(), read(), write(), format(), unlink()}
            \resumeItem {Managed multiple users accessing the same files simultaneously }
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Memory Management (Linux)} $|$ \emph{C}}{April 2020}
          \resumeItemListStart
            \resumeItem{Mimic the functionality of malloc() and free() in C without using any external API }
            \resumeItem {Added functionality like expand, coalesce and release for more efficient Memory Management}
          \resumeItemListEnd  
   
          
      \resumeProjectHeading
          {\textbf{Face vs No-Face Image Classification via Linear Classifier} $|$ \emph{Python, Keras}}{Jan, 2021}
          \resumeItemListStart
            \resumeItem{Gather face images (male, female, child) from different datasets}
            \resumeItem{Gathered no-face images from IMAGENT data set}
            \resumeItem{Simply trained a liner classifier (without non-linearity)}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Male vs Female Image Classification via CNN} $|$ \emph{Python}}{Feb, 2021}
          \resumeItemListStart
            \resumeItem{Gathered small male and image dataset from internet}
            \resumeItem{Trained different NN and CNN architecture and compared the results}
            \resumeItem{Used different training and test data, then improved the accuracy using data augmentation}
          \resumeItemListEnd
    
      \resumeProjectHeading
          {\textbf{Deep Convolutional Generative Adversarial Network (DCGAN)} $|$ \emph{Python, Keras}}{April 2020}
          \resumeItemListStart
            \resumeItem{Assignment of Deep Learning course implemented using Convolutional Layers}
            \resumeItem{Generated images of emojis (with good results) from Apple Emojis Dataset}
            \resumeItem{Designed both generator and discriminator networks}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{kNN Classifier} $|$ \emph{Python}}{July 2020}
          \resumeItemListStart
            \resumeItem{kNN classifier implemented on Iris Data Set}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Naive Bayes Classifier} $|$ \emph{Python}}{June 2020}
          \resumeItemListStart
            \resumeItem{Multi-class classification using Naive Bayes on "Twitter US Airline Sentiment" dataset.}
          \resumeItemListEnd          
          
      \resumeProjectHeading
          {\textbf{Recurrent Neural Network (RNN)} $|$ \emph{Python, Keras}}{May 2020}
          \resumeItemListStart
            \resumeItem{Cleaning the dataset by removing stop words, punctuation, and html tags}
            \resumeItem{Positive/Negative classification of movie reviews from IMDB dataset}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Frequency Domain Filtering} $|$ \emph{MATLAB}}{Nov 2020}
          \resumeItemListStart
            \resumeItem{Created loop-based and vectorized implementation for FFT and IFFT}
            \resumeItem {Applied idead, butterworth and gaussian filter in frequency domain, and compared results}
          \resumeItemListEnd
         
      \resumeProjectHeading
          {\textbf{Content Based Image Retrieval (CBIR)} $|$ \emph{MATLAB}}{Oct 2020}
          \resumeItemListStart
            \resumeItem{Created the database of training images histograms}
            \resumeItem {Compared and retrieved the images based on similar histograms}
            \resumeItem{Also tried equalized image histograms to see if that is a good feature to compare images. Results were negative.}
          \resumeItemListEnd         

      \resumeProjectHeading
          {\textbf{Hidden Markov Model (Bakis Model)} $|$ \emph{Python}}{Nov 2019}
          \resumeItemListStart
            \resumeItem{Applied HHM for part-of-speech prediction in natural language}
          \resumeItemListEnd 

      \resumeProjectHeading
          {\textbf{Binary Independence Model (BIM)} $|$ \emph{Python}}{Oct 2019}
          \resumeItemListStart
            \resumeItem{Applied BIM on corpus of 25000 news articles}
            \resumeItem{With trained BIM, the retrievals were very fast (milliseconds)}
          \resumeItemListEnd 

      \resumeProjectHeading
          {\textbf{Addictive Gem Match Mania (Mobile Game)} $|$ \emph{C\#, Unity Engine}}{Dec 2018 - Nov 2019}
          \resumeItemListStart
            \resumeItem{Match 3 mobile game for Android and iOS}
            \resumeItem{Added core features to the game}
            \resumeItem{Also fixed user reported bugs in the game (with 100000+ users)}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Clothing Classification (Neural Network)} $|$ \emph{MATLAB}}{June 2018}
          \resumeItemListStart
            \resumeItem{Implemented \& designed the architecture of Neural Network from scratch}
            \resumeItem{Implemented Backpropagation algorithm to learn to learn the best color combination of clothes}
            \resumeItem{Semester Project for Computer Vision Course}
          \resumeItemListEnd 

      \resumeProjectHeading
          {\textbf{Handwritten Digit Classification (Neural Network) } $|$ \emph{MATLAB}}{March 2018}
          \resumeItemListStart
            \resumeItem{Implemented \& designed the architecture of Neural Network from scratch to work on MNIST Dataset}
            \resumeItem{Implemented Backpropagation algorithm to learn to learn the best color combination of clothes}
            \resumeItem{Semester Project for Machine Learning Course}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Among the Dead Ones! (Desktop Game)} $|$ \emph{C\#, Unity Engine}}{Feb 2018 - July 2018}
          \resumeItemListStart
            \resumeItem{FPS Survival Shooter game for Desktop platform, worked as a part of my Final Year Project for Undergraduate}
            \resumeItem{Designed and programmed AI Zombies (NPC) for the game.}
            \resumeItem{Extensive work on Unity NavMesh System in collaboration with Unity’s Macanim System to control the root motion of NPC Zombies}
            \resumeItem{Slide-free and accurate pathfinding for zombie character}
            \resumeItem{Ragdoll System to detect bullets with re-animation feature for Zombies \& Audio Collection System with Scriptable Object}
          \resumeItemListEnd 

      \resumeProjectHeading
          {\textbf{CrickSick Scoring Application (Android Application)} $|$ \emph{Android Studio}}{May 2017}
          \resumeItemListStart
            \resumeItem{Application for scoring/recording cricket matches}
            \resumeItem{Simple User Friendly interface to detect all the event of cricket match}
            \resumeItem{Semester project for Software Engineering Course}
          \resumeItemListEnd    
    \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{
    \item{
     {A very good understanding of OPP concepts} \\
     {Extensive knowledge and experience of working in Linux environment and its services (systemd)} \\
     {Familiarity and understanding of relational databases like SQL} \\
     {Very good grasp on logical and structural thinking} \\
     {I have typing speed of \textbf{80 WPM} with querty keyboard \href{https://data.typeracer.com/pit/profile?user=cricketjanoon}{\underline{(typeracer Profile)}} }\\
     \textbf{Languages}{: Python, C, C++, MATLAB, C\#, Java, SQL} \\
     \textbf{Frameworks}{: Keras, TensorFlow, PyTorch} \\
     \textbf{Developer Tools}{: VS Code, CMake, Jupyter Notebook, Git, Visual Studio, SQL Server Management Studio, Linux} \\
     \textbf{Libraries}{: Boost.Asio, POSIX, pandas, NumPy, Matplotlib, OpenCV, Scrappy} }
     }
 \end{itemize}

%-------------------------------------------
\end{document}